---
title: "Assignment-1_Loading-Data-into-a-data-frame"
author: "Paul Perez"
date: "9/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the Mushroom Data Set
```{r}
mushroom_data <- read.csv(file="agaricus-lepiota.data")
```

## Create Mushroom Data Frame
Selected the Class, Habitat, Population, Cap Shape, Cap Surface, Odor, and Bruises columns from the data set as a start to analyzing the different types of mushrooms

```{r}
d <- data.frame(class=mushroom_data[,"p"], habitat=mushroom_data[,"u"], population=mushroom_data[,"s.3"], cap_shape=mushroom_data[,"x"], cap_surface=mushroom_data[,"s"], odor=mushroom_data[,"p.1"],bruises=mushroom_data[,"t"])
```


## Changing the Types of the Columns and Confirming
Running the as.character() to convert the data types to characters.

```{r}
d$class <- as.character(d$class)
d$habitat <- as.character(d$habitat)
d$population <- as.character(d$population)
d$cap_shape <- as.character(d$cap_shape)
d$cap_surface <- as.character(d$cap_surface)
d$odor <- as.character(d$odor)
d$bruises <- as.character(d$bruises)
```

## Change Values in Columns
Adjust names for the Class Column
```{r}
d$class[d$class=="e"]="edible"
d$class[d$class=="p"]="poisonous"
```

Adjust names for the Habitat Column
```{r}
d$habitat[d$habitat=="g"]="grasses"
d$habitat[d$habitat=="l"]="leaves"
d$habitat[d$habitat=="m"]="meadows"
d$habitat[d$habitat=="p"]="paths"
d$habitat[d$habitat=="u"]="urban"
d$habitat[d$habitat=="w"]="waste"
d$habitat[d$habitat=="d"]="woods"
```

Adjust names for the Population Column
```{r}
d$population[d$population=="a"]="abundant"
d$population[d$population=="c"]="clustered"
d$population[d$population=="n"]="numerous"
d$population[d$population=="s"]="scattered"
d$population[d$population=="v"]="several"
d$population[d$population=="y"]="solitary"
```
Adjust names for the Cap Shape Column
```{r}
d$cap_shape[d$cap_shape=="b"]="bell"
d$cap_shape[d$cap_shape=="c"]="conical"
d$cap_shape[d$cap_shape=="x"]="convex"
d$cap_shape[d$cap_shape=="f"]="flat"
d$cap_shape[d$cap_shape=="k"]="knobbed"
d$cap_shape[d$cap_shape=="s"]="sunken"
```
Adjust names for the Cap Surface Column
```{r}
d$cap_surface[d$cap_surface=="f"]="fibrous"
d$cap_surface[d$cap_surface=="g"]="grooves"
d$cap_surface[d$cap_surface=="y"]="scaly"
d$cap_surface[d$cap_surface=="s"]="smooth"
```
Adjust names for the Odor Column
```{r}
d$odor[d$odor=="a"]="almond"
d$odor[d$odor=="l"]="anise"
d$odor[d$odor=="c"]="creosote"
d$odor[d$odor=="y"]="fishy"
d$odor[d$odor=="f"]="foul"
d$odor[d$odor=="m"]="musty"
d$odor[d$odor=="n"]="none"
d$odor[d$odor=="p"]="pungent"
d$odor[d$odor=="s"]="spicy"
```
Adjust names for the Bruises Column
```{r}
d$bruises[d$bruises=="t"]="bruises"
d$bruises[d$bruises=="f"]="no"
```

## Confirm Changes to Data Frame
```{r}
d
View(d)
```

