---
title: "DATA 606 Data Project Proposal"
author: "Paul Perez"
output: html_document
---

### Data Preparation

```{r setup, echo=TRUE, results='hide', warning=FALSE, message=FALSE}
# load data
#install.packages(c("psych", "ggplot2", "DT"))
library(psych)
library(ggplot2)
library(DT)
df <- read.csv("https://raw.githubusercontent.com/ChefPaul/R/master/d606_Project/exam_results.csv", TRUE, ",")
```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**
Does a parents level of education contribute to their child's test outcome?


### Cases 

**What are the cases, and how many are there?**
Each case represents a student from a random selection/generation 



### Data collection 

**Describe the method of data collection.**
The data was found on Kaggle with an additional link for generating a new sample file. These are fictional, randomly generated records for educational purposes only.


### Type of study 

**What type of study is this (observational/experiment)?**
This is an observational study.


### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**
SPScientist. (2018), [Students Performance in Exams](https://www.kaggle.com/spscientist/students-performance-in-exams/metadata)
Kimmons, Royce. (2012), [Understanding digital participation divides](http://roycekimmons.com/tools/generated_data/exams)



### Dependent Variable

**What is the response variable? Is it quantitative or qualitative?**
The dependent variables are the 3 different test scores (math, reading, writing). These are quantitative variables. 



### Independent Variable

**You should have two independent variables, one quantitative and one qualitative.**
There are a few independent variables, but some more important one's to look at are gender, parental level of education, and test preparation course. These are qualitative variables.


### Relevant summary statistics 

**Provide summary statistics for each the variables. Also include appropriate visualizations related to your research question (e.g. scatter plot, boxplots, etc). This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**
### Descriptive Statistics
```{r}
describe(df$math.score)
```
```{r}
describe(df$reading.score)
```
```{r}
describe(df$writing.score)
```
### Counts for each Level of Education
```{r}
table(df$parental.level.of.education)
```

```{r}
datatable(describeBy(df$math.score, group = df$parental.level.of.education, mat = TRUE), rownames = FALSE)
```

```{r}
datatable(describeBy(df$reading.score, group = df$parental.level.of.education, mat = TRUE), rownames = FALSE)
```

```{r}
datatable(describeBy(df$writing.score, group = df$parental.level.of.education, mat = TRUE), rownames = FALSE)
```
## Histograms
### Math Scores
```{r}
ggplot(df, aes(x=math.score)) + geom_histogram()
```
### Reading Scores
```{r}
ggplot(df, aes(x=reading.score)) + geom_histogram()
```
### Writing Scores
```{r}
ggplot(df, aes(x=writing.score)) + geom_histogram()
```

## Next Steps
Based on this intial summary of the data, it looks like there are more cuts of data to look at for a more in depth exploratory anlaysis. It will be interesting to look at other attributes such as gender, race, lunch status and test preparation to see if their are any trends. 