---
title: "d607_Assignment3"
author: "Paul Perez"
date: "9/16/2019"
output: html_document
---
# Question 3
## Task at Hand
Take the raw data below and clean/pull specific data from it.
raw.data <-“555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

## Install Stringr Package
```{r}
library(stringr)
```
Stringr is a package to help aid regular expressions in the R language.

## Pull names from vector
The textbook supplies the string extraction below.
```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

raw_names <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
raw_names
```

## Logic to determine if name has a title
```{r}
title <- str_detect(raw_names, "[[:alpha:]]{2,}\\.")
title
```

## Logic to determine if there is a second name
```{r}
second_name <- str_detect(raw_names, "[A-Z]\\.{1}")
second_name
```

# Question 4
## Describe the types of strings that conform to each regular expression
Identify the types of regular expressions and provide examples

#### a. [0-9]+\\$
This regular expression matches string patterns with numbers ranging between 0-9 one or more times followed by a dollar sign

```{r}
number_vector <- c("Phone Number is:", "1888$", "888$", "$8888")
number_extract <- unlist(str_extract_all(number_vector, "[0-9]+\\$"))
number_extract
```

#### b. \\b[a-z]{1,4}\\b
This regular expression matches words having characters that are lower case appearing 0-4 times

```{r}
characters <- "Bel1eve it or n0t, George isn't 4t home, pl3ase leave a me$$age at the beep"
decipher <- unlist(str_extract_all(characters, "\\b[a-z]{1,4}\\b"))
decipher
```

#### c. .*?\\.txt$
This regular expression matches strings that end with .txt

```{r}
directory_list <- c("assignment_3.txt", "assignment_3.Rmd", "assignment_3.pdf", "assignment_3.html", "assignment_3.Rproj")
txt_files <- unlist(str_extract_all(directory_list, ".*?\\.txt$"))
txt_files
```

#### d. \\d{2}/\\d{2}/\\d{4}
This regular expression matches strings with 2 numbers, followed by "/" and then 2 more numbers followed by "/" and lastly 4 numbers

```{r}
time_stamps <- c("09/14/2019 00:32:34", "12/31/1993 12:25:25", "07/21/1987 18:56:23")
dates <- unlist(str_extract_all(time_stamps, "\\d{2}/\\d{2}/\\d{4}"))
dates
```

#### e. <(.+?)>.+?</\\1>
This regular expression matches the start/end tags with the text inbetween 

```{r}
html <- c("<h1> This is the first header </h1>", "<h2> This is the second header </h2>")
tag <- unlist(str_extract_all(html, "<(.+?)>.+?</\\1>"))
tag
```

# Question 9
## Crack the code below
clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr

```{r}
code <- "clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0TanwoUwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigOd6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
letters <- unlist(str_extract_all(code, "[:alpha:]"))
letters
numbers <- unlist(str_extract_all(code, "[:digit:]"))
numbers
upper_case <- unlist(str_extract_all(code, "[:upper:]"))
upper_case
```

Turns out that upper case characters spelled out "Congratulations You Are A Super Nerd"

[Stringr Cheat Sheet](https://evoldyn.gitlab.io/evomics-2018/ref-sheets/R_strings.pdf)